---
title: "9-Oct-2024"
format: html
editor: visual
---

set up 

```{r}
rm(list = ls())
library(tidyverse)
library(here)
```

laod in dataset

```{r}
tomatos <- read.csv(here("Data", "tomato_data.csv"))
```

slicing data

```{r}
slice(tomatos, c(3,7,9)) |> View()
```

fertalizer treamtment >145g

```{r}
tomatos %>% filter(Treatment == "Fertilizer" & Avg_tomato_weight_g >= 145) |> View()
```

How to create a new output folder
This is used to save intermidiate outputs of data analysis

```{r}
dir.create("Outputs")
```

Writing csv into the new Outputs folder to keep it seperate from base data

```{r}
write.csv(tomatos,here("Outputs","tomatoes_notfixed.csv"),row.names = FALSE)
```

reading back in not fixed tomatoes

```{r}
toms2 <- read.csv(here("Outputs", "tomatoes_notfixed.csv"))
```

## Chapter 3 group_by and summarize()

reading in data

```{r}
lead <- read.csv(here("Data","NoCoLead.csv"))
summary(lead)
```

What if we want to know the average number of tests given in the data set?

```{r}
lead |> summarize(
  mean_num_tests = mean(num_tests)
) |> View()
```

What is the mean number of tests per year?

```{r}
lead_summary <- lead |> 
  group_by(Year) |>
  summarize(mean_tests_per_year = mean(num_tests)
  ) 
```







