---
title: "OneWayAnalysisofVariance"
format: html
editor: visual
---

setting up
```{r}
rm(list=ls())
library(tidyverse)
library(here)
library(ggfortify)
library(multcomp)
```

loading data
```{r}
Forest_dbh <- read.csv(here("Data", "Forest_Tree_DBH_F21.csv"))
```

fixing data types
```{r}
Forest_dbh$Forest <- as.factor(Forest_dbh$Forest)
Forest_dbh$Date <- dmy(Forest_dbh$Date)
```

Making a box wisker plot to get initial look at the variation between forests

1. Is there a difference between mean tree DBH
2. If there is a difference, for which forests does the difference exist
```{r}
ggplot(Forest_dbh, aes(x=Forest, y=DBH_cm))+
  geom_boxplot()+
  geom_jitter(width=0.1)#makes points not on top of each other like point
  theme_bw()
```

Making a model 
```{r}
Model_dbh <- lm(DBH_cm ~ Forest, data = Forest_dbh)
```

Checking the assumptions of the model
```{r}
autoplot(Model_dbh, smooth.colour = NA)
```

Doing the anova model
```{r}
anova(Model_dbh)
```
What are the effects?
```{r}
summary(Model_dbh)
```

Doing a Tukey's HSD (honestly significant difference) test. 
- You ony do one of these tests if there is a significant difference in your response variable. 
mcp means a multiple comparison test
```{r}
PHC1 <- glht(Model_dbh, linfct = mcp(Forest = 'Tukey'))
summary(PHC1)
```
Make it easier to read using compact letter display CLD()
- Any groups that have the same letter are not signifigant from each other. 
```{r}
cld(PHC1)
```
























